Examining False Negatives

### 2023-06-28 TestingPipeline/Scripts/examining_false_positives.Rmd
New figure for proportion vs number of VOGs.

```{r}
getting_viral_set_1 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_tuning_viral=FALSE,
                                tv_1=T, tv_2=T, tv_3=T, tv_4=T,
                                include_tuning_not_viral=FALSE,
                                ntv_1=T, ntv_2=T, ntv_3=T, ntv_4=T, ntv_5=F,
                                include_virsorter=FALSE) {

@@

```{r}
head(annotations_vb)
```
```{r}
table(annotations_vb$contig %in% fp_bacteria_list)
table(annotations_vb$contig %in% fp_plasmid_list)
```

@@

```{r}
ggplot(annotations_vb_fp_vog_count, 
       aes(x=seqtype, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_boxplot() +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Sequence Type") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.5)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1)) +
  facet_wrap(~confusion_matrix, scales="free_x")
```
```{r}
t.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="bacteria"],
       annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="virus"])
```
```{r}
t.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="plasmid"],
       annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="virus"])
```

```{r}
ggplot(annotations_vb_fp_vog_count, 
       aes(x=num_vog, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Number of VOGs") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.5)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1))
```

@@

```{r}
ggplot(viruses, aes(y=percent_viral, x=confusion_matrix_high_MCC)) +
  geom_boxplot() +
  geom_point() +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") 
```
```{r}
table(viruses$confusion_matrix_high_MCC[viruses$checkv_length>=5000])
```

>>>>

```{r getting_viral_set_1}
getting_viral_set_1 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_tuning_viral=FALSE,
                                tv_1=T, tv_2=T, tv_3=T, tv_4=T,
                                include_tuning_not_viral=FALSE,
                                ntv_1=T, ntv_2=T, ntv_3=T, ntv_4=T, ntv_5=F,
                                include_virsorter=FALSE) {

@@

```{r}
head(annotations_vb)
```

```{r}
table(annotations_vb$contig %in% fp_bacteria_list)
table(annotations_vb$contig %in% fp_plasmid_list)
```

@@

```{r}
ggplot(annotations_vb_fp_vog_count, 
       aes(x=seqtype, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_boxplot() +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Sequence Type") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.5)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1)) +
  facet_wrap(~confusion_matrix, scales="free_x")
```

```{r}
t.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="bacteria"],
       annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="virus"])
```

```{r}
t.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="plasmid"],
       annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="virus"])
```

```{r}
ggplot(annotations_vb_fp_vog_count, 
       aes(x=num_vog, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_smooth(formula = y ~ log(x), se=F) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Number of VOGs") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.2)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1)) +
  facet_wrap(~seqtype, scales="free_x") +
  ylim(c(0,1))

ggplot(annotations_vb_fp_vog_count, 
       aes(x=num_vog, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_smooth(method="lm", se=F) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Number of VOGs") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.2)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1)) +
  facet_wrap(~seqtype, scales="free_x") +
  ylim(c(0,1))

ggplot(annotations_vb_fp_vog_count, 
       aes(x=num_vog, y=prop_vog, 
           color=seqtype, fill=seqtype)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Proportion Genes VOGs") +
  xlab("Number of VOGs") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(3)), 0.2)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(3)), 1)) +
  facet_wrap(~seqtype, scales="free_x") +
  ylim(c(0,1))
```

```{r}

cor.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="bacteria"], annotations_vb_fp_vog_count$num_vog[annotations_vb_fp_vog_count$seqtype=="bacteria"])

cor.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="virus"], annotations_vb_fp_vog_count$num_vog[annotations_vb_fp_vog_count$seqtype=="virus"])

cor.test(annotations_vb_fp_vog_count$prop_vog[annotations_vb_fp_vog_count$seqtype=="plasmid"], annotations_vb_fp_vog_count$num_vog[annotations_vb_fp_vog_count$seqtype=="plasmid"])
```

@@

```{r}
ggplot(viruses, aes(y=percent_viral, x=confusion_matrix_high_MCC)) +
  geom_boxplot() +
  geom_point() +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") 
```

```{r}
table(viruses$confusion_matrix_high_MCC[viruses$checkv_length>=5000])
```
